### 2021-02-12 main.tex
Remove an accidentally inserted URL
Add a todo

\begin{abstract}
\input{abstract}https://www.overleaf.com/project/5f75a50ba1a0930001ce1162
\end{abstract}

@@

\subsection{Loss function} \todo{MS: tady jsem zatim skoncil...}
\label{sec:loss}

@@

Given a problem $P$, a symbol cost model $c : \cnf \to \re^*$
\todo{Confusing?}
returns a vector of costs of the symbols of $P$:
$$
c(P) = (c_1, \ldots, c_n)
$$

Let $\Prec \in \Perm{n}$ be a precedence of symbols of problem $P$.
Let $k(n) = \frac{2}{n(n+1)}$ be a normalization factor for precedences of length $n$.
The symbol cost model $c$ can be extended to a precedence cost model $C$
by taking the weighted sum of symbol costs:
$$
C(\Prec | P)
= k(n) \sum_{i=1}^n c_{\Prec_i} \cdot i
= k(n) \sum_{i=1}^n c_i \cdot \inv{\Prec}_i
= k(n) \DotProd{c(P)}{\inv{\Prec}}
$$
Note that the value of $C$ is minimized by a precedence that orders the symbols by their costs in non-increasing order.
\todo{Discuss, prove.}

Fixing the normalization factor $k(n)$ to the value $\frac{2}{n(n+1)}$
ensures that costs of precedences of various lengths are commensurable.
Observe namely that if $c$ assigns each symbol the same cost $c_0$,
then the precedence cost is equal to $c_0$ irrespective of the signature length $n$:
\begin{equation} \label{eq:model_cost}
C(\Prec | P) = \frac{2}{n(n+1)} \sum_{i=1}^n c_0 \cdot i = c_0
\end{equation}

Let $\PrecBetter, \PrecWorse \in \Perm{n}$ be two symbol precedences over $P$.
Let $\PrecBetter$ yield a faster proof search on $P$ than $\PrecWorse$, denoted as $\Better{\PrecBetter}{\PrecWorse}$.
The precedence cost model can be extended to predict the probability that $\PrecBetter$ is better than $\PrecWorse$:
\todo{Fix this. Ensure the polarity is sound.}
\begin{align*}
p(\Better{\PrecBetter}{\PrecWorse} | P)
&= \sigmoid \SquareBracket{C(\PrecWorse | P) - C(\PrecBetter | P)} \\
%&= \sigmoid \SquareBracket{k(n) \sum_{i=1}^n c_i \cdot (\inv{\PrecWorse}_i - \inv{\PrecBetter}_i)} \\
&= \sigmoid \SquareBracket{k(n) \DotProd{c(P)}{\inv{\PrecWorse} - \inv{\PrecBetter}}}
\end{align*}
It is easy to see\todo{MS: Bez znalosti $\sigmoid$ uplne ne ;)} that $p(\Better{\PrecBetter}{\PrecWorse} | P) > 0.5$ if and only if $C(\PrecWorse | P) > C(\PrecBetter | P)$,
and that the value of $p$ can be increased by increasing $C(\PrecWorse | P)$ or decreasing $C(\PrecBetter | P)$.

@@

Every \gls{cnf} problem can be represented by a \gls{hin} with the network schema shown in \cref{fig:CnfSchema}.\todo{MS: Mel jsem chut to opravit na velke "Fig.", ale s makrem se mi hadat nechce ;)}
% Cite: https://www.kdd.org/exploration_files/V14-02-03-Sun.pdf
% Referenced from: https://docs.dgl.ai/en/0.5.x/generated/dgl.DGLHeteroGraph.metagraph.html

@@

When presented with a \gls{cnf} problem $P$ with signature $\symbols$,
the recommender produces a precedence $\pi$ of symbols from $\symbols$.
In order to generate the precedence,
the recommender first assigns a cost value to each symbol
by invoking a symbol cost model (a trained \gls{gcn}) on a graph representation of $P$.
Ordering the symbols by their predicted costs in nondecreasing order yields the precedence $\pi$.

@@

The training is performed using a fixed \acrlong{atp}.
The configuration of the prover,
including for example saturation algorithm, age-weight ratio, and term ordering scheme,
is arbitrary\todo{MS: tohle slovo je prilis silny. Veta by spis mela vysvetlit, ze jsme si neco vybrali, protoze je nam to v postate jedno. Ale zaroven si uvedomujeme, ze to nejak ovlivni vysledek a ze v ultimatnim super-toolu, by se na vsech ostatni paramatrech dalo conditionovat.} and fixed.
The prover needs to support refutational reasoning on \gls{cnf} problems
and use a term simplification ordering parameterized by a symbol precedence.
For example, the \glspl{atp} \vampire{} and E satisfy this requirement.
Note that both of these provers support the \gls{kbo} and \gls{lpo} term simplification ordering schemes,
and that each of these schemes is parameterized by a symbol precedence.

@@

We model the probability of the event "$\pi_0$ is better than $\pi_1$"
by the sigmoid of $\CostPrecPair(\pi_0, \pi_1)$:
$$
p(\pi_0, \pi_1) = \sigmoid(\CostPrecPair(\pi_0, \pi_1))
$$

@@

This work was supported by
the Czech Science Foundation project 20-06390Y
and
the Grant Agency of the Czech Technical University in Prague, grant\\
no.~SGS20/215/OHK3/3T/37.

>>>>

\begin{abstract}
\input{abstract}
\end{abstract}

@@

\subsection{Loss function} 
\label{sec:loss}

@@

Given a problem $P$, a symbol cost model 
\todo{MS: Zvidavy invalida Jirka Karasek: a co ze je to ten model? 
Mohl byste to to prosim nekde driv vysvetlit?}
$c : \cnf \to \re^*$
\todo{MS: Mozna by se dalo zbavit lehce podivneho $\re^*$ tim,
ze model bude funkce $(P \in \cnf, s \in \Sigma_P) \to \re$?
Zas pak nepujde pouzivat zapis skalarniho soucinu; hmmm.}
returns a vector of costs of the symbols of $P$:
$$
c(P) = (c_1, \ldots, c_n)
$$

Let $\Prec \in \Perm{n}$ be a precedence of symbols of problem $P$.
Let $k(n) = \frac{2}{n(n+1)}$ be a normalization factor for precedences of length $n$.
The symbol cost model $c$ can be extended to a precedence cost model $C$
by taking the weighted sum of symbol costs:
\begin{equation} \label{eq:model_cost}
C(\Prec | P)
= k(n) \sum_{i=1}^n c_{\Prec_i} \cdot i
= k(n) \sum_{i=1}^n c_i \cdot \inv{\Prec}_i
= k(n) \DotProd{c(P)}{\inv{\Prec}}
\end{equation}
Note that the value of $C$ is minimized by a precedence that orders the symbols by their costs in non-increasing order.
\todo{Discuss, prove.}
\todo{Mention here that minimizing C yields the best precedence.}

Fixing the normalization factor $k(n)$ to the value $\frac{2}{n(n+1)}$
ensures that costs of precedences of various lengths are commensurable.
Observe namely that if $c$ assigns each symbol the same cost $c_0$,
then the precedence cost is equal to $c_0$ irrespective of the signature length $n$:
$$
C(\Prec | P) = \frac{2}{n(n+1)} \sum_{i=1}^n c_0 \cdot i = c_0
$$

Let $\PrecBetter, \PrecWorse \in \Perm{n}$ be two symbol precedences over $P$.
Let $\PrecBetter$ yield a faster proof search on $P$ than $\PrecWorse$, denoted as $\Better{\PrecBetter}{\PrecWorse}$.
The precedence cost model can be extended to predict the probability that $\PrecBetter$ is better than $\PrecWorse$:
\todo{Fix this. Ensure the polarity is sound.}
\todo{MS: zatim chybi vysvetleni $\sigmoid$.}
\todo{MS: duvod proc mi v tomhle kontextu moc nesedi mluvit o pravdepodobnosti
je ten, ze bez dalsiho vysvetlovani to vypada, ze si myslime, ze
kdyz pomoci $\sigmoid$ splacnem v podstate libovolne hodnoty do
intervalu $(0,1)$, zecne to automaticky fungovat jako pravdepodobnost.}
\begin{align*}
p(\Better{\PrecBetter}{\PrecWorse} | P)
&= \sigmoid \SquareBracket{C(\PrecWorse | P) - C(\PrecBetter | P)} \\
%&= \sigmoid \SquareBracket{k(n) \sum_{i=1}^n c_i \cdot (\inv{\PrecWorse}_i - \inv{\PrecBetter}_i)} \\
&= \sigmoid \SquareBracket{k(n) \DotProd{c(P)}{\inv{\PrecWorse} - \inv{\PrecBetter}}}
\end{align*}
It is easy to see that $p(\Better{\PrecBetter}{\PrecWorse} | P) > 0.5$ if and only if $C(\PrecWorse | P) > C(\PrecBetter | P)$,
and that the value of $p$ can be increased by increasing $C(\PrecWorse | P)$ or decreasing $C(\PrecBetter | P)$.

@@

\todo{MS: HIN bych povazoval za pro CADE-people neznamuy pojem.
Bude treba uvest aspon jednou vetou. Mozna neco citovat?}

Every \gls{cnf} problem can be represented by a \gls{hin} with the network schema shown in \cref{fig:CnfSchema}.\todo{MS: Mel jsem chut to opravit na velke "Fig.", ale s makrem se mi hadat nechce ;)}
% Cite: https://www.kdd.org/exploration_files/V14-02-03-Sun.pdf
% Referenced from: https://docs.dgl.ai/en/0.5.x/generated/dgl.DGLHeteroGraph.metagraph.html
\todo{MS: Filosoficka k ``can be represented''; mozna by se mohlo nekde objevit:
Snazime se do struktury HIN ``otisknout'' celou strukturu CNF (jak jsem rikal,
znamena to, ze zobrazeni je proste), abychom siti nevzali moznost ``vedet o problemu
uplne vsechno'' (az na veci, na kterych nezalezi jako poradi literaly v klauzulich, etc).
Ta filosoficka poznamka je o tom, ze pro dobre uceni tohle vlastne vubec nemusi byt treba,
ze nejaky ``hrubsi otisk'' by mohl stacit tez (a byt treba mensi),
ale my nevime, jak takovy zvolit. }

@@

When presented with a \gls{cnf} problem $P$ with signature $\symbols$,
the recommender produces a precedence $\pi$ of symbols from $\symbols$.
\todo{MS: proc nepouzivat znaceni z predchoziho clanku, kdy $P = (\symbols,\mathit{Cl})$?}
In order to generate the precedence,
the recommender first assigns a cost value to each symbol
by invoking a symbol cost model (a trained \gls{gcn}) on a graph representation of $P$.
Ordering the symbols by their predicted costs in nondecreasing order yields the precedence $\pi$.

@@

The training is performed using a fixed \acrlong{atp}.
\todo{MS: zase spis preferuj cinny rod. A klidne muzes proste rict, ze pouzivame vampira :)}
The configuration of the prover,
including for example saturation algorithm, age-weight ratio, and term ordering scheme,
is arbitrary\todo{MS: tohle slovo je prilis silny. Veta by spis mela vysvetlit, ze jsme si neco vybrali, protoze je nam to v postate jedno. Ale zaroven si uvedomujeme, ze to nejak ovlivni vysledek a ze v ultimatnim super-toolu, by se na vsech ostatni paramatrech dalo conditionovat.} and fixed.
The prover needs to support refutational reasoning on \gls{cnf} problems
and use a term simplification ordering parameterized by a symbol precedence.
For example, the \glspl{atp} \vampire{} and E satisfy this requirement.
Note that both of these provers support the \gls{kbo} and \gls{lpo} term simplification ordering schemes,
and that each of these schemes is parameterized by a symbol precedence.
\todo{MS: Jak jsme se o tom bavili; v ramvi Occamovky neni treba zminovat LPO.}

@@

We model the probability of the event ``$\pi_0$ is better than $\pi_1$''
by the sigmoid of $\CostPrecPair(\pi_0, \pi_1)$:
$$
p(\pi_0, \pi_1) = \sigmoid(\CostPrecPair(\pi_0, \pi_1))
$$

@@

\todo{MS: zvazit, jestli nerozepsat zvlast Martin, zvlast Filip.
Pripadne se zeptat Hanky, jestli bychom nemeli nejak vypichnout
jen GACR.}

This work was supported by
the Czech Science Foundation project 20-06390Y,
the project RICAIP no. 857306 under the EU-H2020 programme,
and
the Grant Agency of the Czech Technical University in Prague, grant\\
no.~SGS20/215/OHK3/3T/37.
